Predicting the PCG PSeudo-Random Number Generator In Practice

### 2020-05-28 article/main.tex
tables aux bon endroits
début 5.3

\subsection{Part 2 : Récupération de la différence complète et deuxième filtre}
On calcule préalalement H matrice génératrice du réseau $\mathcal{L}(A,2^{128 - \ell},m)$ réduite par la méthode LLL.
On a récupéré de la Part 1 une série de $S_0[0 : \ell]$, $r_i$ (i = 0, ..., n) et $C[0 : \ell]$ parmi lequels se trouve notre solution.
\begin{enumerate}
  \item recupérer toutes les $r_i$ possibles, pour $n \leq i \leq m$  par la même méthode que l'étape 3 de la Part 1, répétée $m-n$ fois. On garde en mémoire toutes les rotations possiles.
  \item Pour chacune des $r$ possibles
  \begin{enumerate}
    \item We cumpute $r'$ et $\Delta r$ avec le même méthode que pour $\Delta T$ : 
    \begin{align}
      r'_i = r_i - (A^i*S_0[0 : \ell] + C[0 : \ell] * \sum_{j = 0}^i A^j)[64 - 6 : 64 + \ell])[122 : 128]
      \Delta r_i &= r_{i+1} - r_i
    \end{align}

    \item We get the correspondant $\Delta S'_0S'_1$ ($S'$ dont on aurait retiré que la composante en $C[0 : \ell]$ et non en $C$ entier) computing $\texttt{CVP}(r * 2^{128 - \ell}, \mathcal{L}(A,2^{128 - \ell},m))$. We use the fpylll python library CVP function. On stocke le $DS_0S_1$ correspondant.

    \item \todo{parler du problème de retenue étrange}

  \end{enumerate}
\end{enumerate}

\subsection{preuve cas difficile}
\todo{À ranger au bon endroit}
% Babai ça marche pas (genre zero)

The vector \(S'\) has been constructed such that it is in \(L(A,2^{128},n)\) and its \(\ell\) lower bits are zero.

We call \(U\) the truncated vector : \(S'[\ell,128]\). We notice that \(U\) is in \(L(A,2^{128-\ell},n)\).

We consider the case were we successfully guessed the 6 upper bits of each \(S_i\) and the \(\ell\) lower bits of \(S_0\). Then we know the 6 upper bits of \(U\).

(maybe dessin)

We consider the vector \(T'\) computed in step (numerodelastepenquestion). To recover \(U\), we use an exact CVP solver as explain in  (insererlasection) on \(T'\) and \(L(A,2^{128-\ell},n)\).

As \(U\) and \(T'\) have exactly the same \(6\) upper bits  know that \(\lVert U-T \rVert \leqslant \sqrt{n2^{2(128-6-\ell)}}\).

So, to be sure that our algorithm return the vector \(U\), we need to find sets of parameters \((n,\ell)\) such that :

\[2\sqrt{n}^{(128-6-\ell)} \leqslant \lVert SVP(L(A,2^{128-\ell},n))\rVert \]

\begin{itemize}
	\item For \(\ell=11\), the smallest \(n\) we need is 39.

	\item For \(\ell=12\), the smallest \(n\) we need is 38.

	\item For \(\ell=13\), the smallest \(n\) we need is again 38 .

\end{itemize}

\begin{theorem}
  The algorithm described above works with probability.... in time ...
\end{theorem}

\section{Implementation and Practical Results}

>>>>

% \subsection{preuve cas difficile}
% \todo{À ranger au bon endroit}
% % Babai ça marche pas (genre zero)

% The vector \(S'\) has been constructed such that it is in \(L(A,2^{128},n)\) and its \(\ell\) lower bits are zero.

% We call \(U\) the truncated vector : \(S'[\ell,128]\). We notice that \(U\) is in \(L(A,2^{128-\ell},n)\).

% We consider the case were we successfully guessed the 6 upper bits of each \(S_i\) and the \(\ell\) lower bits of \(S_0\). Then we know the 6 upper bits of \(U\).

% (maybe dessin)

% We consider the vector \(T'\) computed in step (numerodelastepenquestion). To recover \(U\), we use an exact CVP solver as explain in  (insererlasection) on \(T'\) and \(L(A,2^{128-\ell},n)\).

% As \(U\) and \(T'\) have exactly the same \(6\) upper bits  know that \(\lVert U-T \rVert \leqslant \sqrt{n2^{2(128-6-\ell)}}\).

% So, to be sure that our algorithm return the vector \(U\), we need to find sets of parameters \((n,\ell)\) such that :

% \[2\sqrt{n}^{(128-6-\ell)} \leqslant \lVert SVP(L(A,2^{128-\ell},n))\rVert \]

% \begin{itemize}
% 	\item For \(\ell=11\), the smallest \(n\) we need is 39.

% 	\item For \(\ell=12\), the smallest \(n\) we need is 38.

% 	\item For \(\ell=13\), the smallest \(n\) we need is again 38 .

% \end{itemize}

% \begin{theorem}
%   The algorithm described above works with probability.... in time ...
% \end{theorem}

\subsection{Complete State Reconstruction}

Once all the rotations have be recovered and $\Delta S_0$ has been found
entirely, the only thing that remain is to actually find the entire $S_0$. For
this, we use again eq.~\eqref{eq:output}. For this we use the fact that there is
an (unknown) \emph{carry} $0\leq \gamma_i \leq 1$ such that:
\begin{align*}
  S_i[0:64] &= S_0[0:64] \boxplus \nabla S_i[0:64] \\
  S_i[64:128] &= S_0[64:128] \boxplus \nabla S_i[64:128] \boxplus \gamma_i \\
\end{align*}
This therefore gives:
\[
  X_i  \lll r_i = \bigl(S_0[0:64] \boxplus \nabla S_i[0:64]\bigr) \oplus \bigl(S_0[64:128] \boxplus \nabla S_i[64:128] \boxplus \gamma_i\bigr).
\]
\section{Implementation and Practical Results}
